\documentclass{writeup}

\begin{document}
\tagged{greedy}

\begin{solutions}
  \begin{solution}{The ultimate greedy solution}{n!}{n}
    The ultimate naive solution is to try every possible configuration of boats, check whether it's valid and keep the one with the most boats assigned to their ring.
    This is not trivial to code as it would require some recursion to construct the cross product of sets of possible boat positions.
    This would require $O(n!)$ time and is therefore not feasable for large $n$.
  \end{solution}
  
  \begin{solution}{A naive greedy solution}{n^2\log{n}}{1}
    In the naive solution we will place boats from left to right.
    Greedily taking the boat that can be assigned to the ring leaving the most space after it gives us a correct solution.
    To implement this we have to sort the remaining boats by their rightmost point after possible assignment and pick the best one every time.

    \code{naive}{6}{32}
  \end{solution}

  \begin{solution}{A better solution}{n}{1}
    Because the above greedy solution is correct, eventhough it is too slow, we can use it in a proof.
    To build a better solution, first we have to realise that if we want to place a new boat, and it would require replacing two previous boats, that boat can never appear in an optimal solution.
    In this situation we would be looking at boats from left to right according to their assigned rings.
    This means that we can keep track of the rightmost points of the previous two boats that were placed.
    \code{main}{15}{21}
    If the next boat we check doesnt' collide with any of the previous two boats, we can just place the boat.
    \code{main}{22}{25}
    If it collides with the last boat and would take up less space, we replace it.
    \code{main}{26}{34}
    In both of these situations the new boat has to be in the optimal solution.
  \end{solution}
\end{solutions}



\end{document}
